Enforced Invariant Confluence

### 2018-03-04 doc/paper_redux/iconfluence.tex
Revised everything with new s_0, T, I definitions.

\section{\Iconfluence{}}
In this section, we present six different ways to think about \Iconfluence{}:
three state-based approaches and three operation-based approaches.

\subsection{State-Based}
\begin{definition}
  A \defword{distributed state-based object} $O$ is a triple $(S, s_0, \join)$
  where $S$ is a set of states, $s_0 \in S$ is a designated start state, and
  $\join: S \times S \to S$ is a binary merge operator that we call join.
\end{definition}

@@

\begin{example}
  $(\nats, 0, +)$ is a distributed object, $t(x) = 2x$ is a transaction, and
  $\setst{x \in \nats}{\text{$x$ is even}}$ is an invariant. Here, $I(0)$ and
  $I(2)$ but $\lnot I(1)$ and $\lnot I(3)$.
\end{example}

There are three ways to think about state-based \Iconfluence{}: a process-based
approach, a graph-based approach, and an expression-based approach. Below, we
describe the process-based approach and the graph-based approach informally and
describe the expression-based approach formally. All three approaches are
illustrated in \figref{StateBasedModels}.

@@

\subsubsection{Process-Based}
The process-based model is most similar to the process model described by
Shapiro et al.\ in~\cite{shapiro2011conflict}. We are given a state-based
object $O = (S, s_0, \join)$, a set of transactions $T$, an invariant $I$, and
a set $\seq{p}{1}{n}$ of $n$ processors. Each processor begins with state
$s_0$. A processor $p_i$ can perform one of two actions.

@@

$(O, T)$ is invariant-confluent with respect to $I$ (abbreviated \Iconfluent{})
if every reachable state (including $s_0$) satisfies the invariant. Note that
this definition of \Iconfluence{} is different from the original definition
in~\cite{bailis2014coordination}. Later, we will see that they are equivalent.

\subsubsection{Graph-Based}
The graph-based approach is most similar to the model used by Bailis et al.\
in~\cite{bailis2014coordination}. We are given a directed acyclic graph where
vertices are states, and edges are either labelled with transactions or are
unlabelled if they correspond to a join. The graph is really just an alternate
way of representing an execution in the process-based model, but with duplicate
states collapsed into a single vertex. As with the process-based model, we say
that $(O, T)$ is \Iconfluent{} if every vertex in every graph satisfies the
invariant.

\subsubsection{Expression-Based}
The expression-based approach formalizes the process-based and graph-based
approach using expressions. Given a state based object $O = (S, s_0, \join)$
and a set of transactions $T$, we consider expressions generated by the
following grammar:
\[
  e ::= s_0 \mid t(e) \mid e_1 \join e_2
\]
where $t$ corresponds to a transaction in $T$. We can evaluate an expression
$e$, written $eval(e)$, in the obvious way:
\begin{mathpar}
  eval(s_0) \defeq s_0

@@

\begin{definition}
  Intuitively, we say an expression is \defword{reachable} if it can be reached
  in an execution of the process-based model. Formally, we defined a predicate
  $\reachable{\cdot}$ as follows:

  \begin{mathpar}
    \inferrule{ }{\reachable{s_0}}

    \inferrule{\reachable{e} \\ I(t(e))}{\reachable{t(e})}

    \inferrule{\reachable{e_1} \\ \reachable{e_2}}{\reachable{e_1 \join e_2}}
  \end{mathpar}
\end{definition}

\begin{definition}
  $(O, T)$ is \defword{\Iconfluent{}} if $\setst{e}{\reachable{e}} \subseteq
  I$. In other words, $T$ is \Iconfluent{} if all reachable states satisfy the
  invariant.
\end{definition}

As we mentioned earlier, this definition of \Iconfluence{} is different than
the original definition presented in~\cite{bailis2014coordination} (though it
is the same as the definition in~\cite{gotsman2016cause}), but they are
(almost) equivalent. We introduce some definitions and then prove this.

@@

Bailis et al.\ defined \Iconfluence{} to mean that expressions recursively
satisfying $I$ are closed under join. That is, $(O, T)$ is \Iconfluent{} if
\[
  \forall e_1, e_2.\; \Irec{e_1} \land \Irec{e_2} \implies I(e_1 \join e_2)
\]
If $\lnot I(s_0)$, then \Iconfluence{} holds vacuously which is a bit silly, so
Bailis et al.\ probably ought to have also added the condition $I(s_0)$ to
their definition of \Iconfluence{}. Doing so, the two definitions become
equivalent.

\begin{lemma}\lemlabel{StateBasedIrecImpliesReachable}
  $\Irec{e} \implies \reachable{e}$
\end{lemma}
\begin{elidableproof}
  We perform structural induction on $e$.
  \begin{itemize}
    \item \textbf{Case $s_0$.}
      Axiomatically, $\reachable{s_0}$.

    \item \textbf{Case $t(e)$.}
      $\Irec{t(e)}$, so $I(t(e))$ and $\Irec{e}$. By the inductive hypothesis,
      $\reachable{e}$, so by the definition of $\reachable{\cdot}$,
      $\reachable{t(e)}$.

    \item \textbf{Case $e_1 \join e_2$.}
      $\Irec{t(e)}$, so $\Irec{e_1}$ and $\Irec{e_2}$. By the inductive
      hypothesis, $\reachable{e_1}$ and $\reachable{e_2}$, so by the definition
      of $\reachable{\cdot}$, $\reachable{e_1 \join e_2}$.
  \end{itemize}
\end{elidableproof}

\begin{claim}\clmlabel{StateBasedTwoIconfluenceDefs}
  Consider a state based object $O = (S, s_0, \join)$, a set of transactions
  $T$, and an invariant $I$. The following two are equivalent:
  \begin{enumerate}[\quad(1)]
    \item
      $\setst{e}{\reachable{e}} \subseteq I$

    \item
      $I(s_0)$ and $\Irec{e_1} \land \Irec{e_2} \implies I(e_1 \join e_2)$
  \end{enumerate}
\end{claim}
\begin{elidableproof}
  First, we show that (1) implies (2). Axiomatically, $\reachable{s_0}$, so by
  (1), $I(s_0)$. Let $e_1$ and $e_2$ be arbitrary expressions such that
  $\Irec{e_1}$ and $\Irec{e_2}$. By \lemref{StateBasedIrecImpliesReachable},
  $\reachable{e_1}$ and $\reachable{e_2}$. Thus, $\reachable{e_1 \join e_2}$,
  so by (1), $I(e_1 \join e_2)$.

  Next, we show that (2) implies (1). We prove by structural induction that for
  all $e$, $\reachable{e} \implies \Irec{e}$. From this, (1) is immediate.
  \begin{itemize}
    \item \textbf{Case $s_0$.}
      $I(s_0)$ by (2), so $\Irec{s_0}$

    \item \textbf{Case $t(e)$.}
      $\reachable{t(e)}$, so $\reachable{e}$ and $I(t(e))$. By the inductive
      hypothesis, $\Irec{e}$, so by the definition of $\Irec{\cdot}$,
      $\Irec{t(e)}$.

    \item \textbf{Case $e_1 \join e_2$.}
      $\reachable{e_1 \join e_2}$, so $\reachable{e_1}$ and $\reachable{e_2}$.
      By the inductive hypothesis, $\Irec{e_1}$ and $\Irec{e_2}$. By $(2)$,
      $I(e_1 \join e_2)$. Thus, $\Irec{e_1 \join e_2}$.
  \end{itemize}
\end{elidableproof}

\subsection{Operation-Based}
\begin{definition}
  A \defword{distributed operation-based object} is a pair $O = (S, s_0)$ where
  $S$ is a set of states and $s_0 \in S$ is a designated start state.
\end{definition}

@@

\begin{example}
  $(\nats, 0)$ is a distributed object. $t(x) = \lambda y.\ x + y$ is a
  transaction that given a state $x$ returns a function $\lambda y.\ x + y$
  that adds $x$ to its argument. $\setst{x \in \nats}{x \geq 0}$ is an
  invariant.
\end{example}

As with state-based objects, there are three ways to think about
operation-based \Iconfluence{}: a process-based approach, a graph-based
approach, and an expression-based approach. All three approaches are
illustrated in \figref{OpBasedModels} and are described in more detail below.

@@

\subsubsection{Process-Based}
As with the state-based approach, the process-based model is most similar to
the process model described by Shapiro et al.\ in~\cite{shapiro2011conflict}.
We are given an operation-based object $O$, a set of transactions $T$, an
invariant $I$, and a set $\seq{p}{1}{n}$ of $n$ processors. Each processors
begins with state $s_0$. A processor $p_i$ can do one of two things.

@@

  \item
    $p_i$ can receive a broadcasted shadow transaction $t(s_j)$ from some other
    processor $p_j$. When $p_i$ receives $t(s_j)$, it transitions from its
    state $s_i$ to state $t(s_j)(s_i)$. When $p_i$ receives a shadow
    transaction, it must execute it, even if $\lnot I(t(s_j)(s_i))$.
\end{itemize}

$(O, T)$ is \Iconfluent{} if every reachable state (including $s_0$) satisfies
the invariant.

\subsubsection{Graph-Based}
In the graph-based model, we are given a directed acyclic graph in which each
vertex is a state $s$ and each edge is labelled with a shadow operation $t(s)$
where $s$ is some other vertex in the graph. $(O, T)$ is \Iconfluent{} if every
vertex in every graph satisfies $I$.

\subsubsection{Expression-Based}
Given an operation-based object $O = (S, s_0)$ and a set of transactions $T$,
we consider expressions built from the following grammar:
\[
  e ::= s_0 \mid t(e_1)(e_2)
\]
where $t$ corresponds to a transaction in $T$. We can evaluate an expression,
denoted $eval(e)$, in the obvious way:
\begin{mathpar}
  eval(s_0) \defeq s_0

@@

\begin{definition}
  As with state-based expressions, we formalize which operation-based
  expressions are reachable.

  \begin{mathpar}
    \inferrule{ }{\reachable{s_0}}

    \inferrule{
      \reachable{e_1} \\
      \reachable{e_2} \\
      I(t(e_1)(e_1))
    }{\reachable{t(e_1)(e_2)}}
  \end{mathpar}
\end{definition}

\begin{definition}
  $(O, T)$ is \defword{\Iconfluent{}} if $\setst{e}{\reachable{e}} \subseteq
  I$.
\end{definition}

As with state-based objects, we have an equivalent definition of \Iconfluence{}
that deals with the closure of recursively invariant satisfying states.

@@

\begin{lemma}\lemlabel{OpBasedIrecImpliesReachable}
  $\Irec{e} \implies \reachable{e}$
\end{lemma}
\begin{elidableproof}
  We perform a structural induction on $e$.
  \begin{itemize}
    \item \textbf{Case $s_0$.}
      Axiomatically, $\reachable{s_0}$.

    \item \textbf{Case $t(e_1)(e_2)$.}
      $\Irec{t(e_1)(e_2)}$, so $\Irec{e_1}$, $\Irec{e_2}$, and
      $I(t(e_1)(e_1))$. By the inductive hypothesis, $\reachable{e_1}$ and
      $\reachable{e_2}$. Thus, $\reachable{t(e_1)(e_2)}$.
  \end{itemize}
\end{elidableproof}

\begin{claim}\clmlabel{OpBasedTwoIconfluenceDefs}
  Given an operation-based object $(S, s_0)$, a set of transactions $T$, and an
  invariant $I$, the following two are equivalent:
  \begin{enumerate}[\quad(1)]
    \item
      $\setst{e}{\reachable{e}} \subseteq I$

    \item
      $I(s_0)$ and $\Irec{e_1} \land \Irec{e_2} \land I(t(e_1)(e_1)) \implies
      I(t(e_1)(e_2))$.
  \end{enumerate}
\end{claim}
\begin{elidableproof}
  First, we show that (1) implies (2). $\reachable{s_0}$, so by (1), $I(s_0)$.
  Let $e_1$ and $e_2$ be arbitrary expressions such that $\Irec{e_1}$,
  $\Irec{e_2}$, and $I(t(e_1)(e_1))$. By \lemref{OpBasedIrecImpliesReachable},
  $\reachable{e_1}$ and $\reachable{e_2}$, so $\reachable{t(e_1)(e_2)}$. By
  (1), $I(t(e_1)(e_2))$.

  Next, we show that (2) implies (1). We show by structural induction on $e$
  that $\reachable{e} \implies \Irec{e}$. From this, (1) is immediate.
  \begin{itemize}
    \item \textbf{Case $s_0$.}
      By (2), $I(s_0)$, so $\Irec{s_0}$.

    \item \textbf{Case $t(e_1)(e_2)$.}
      $\reachable{t(e_1)(e_2)}$, so $\reachable{e_1}$, $\reachable{e_2}$, and
      $I(t(e_1)(e_1))$. By the inductive hypothesis, $\Irec{e_1}$ and
      $\Irec{e_2}$. By (2), $I(t(e_1)(e_2))$, so $\Irec{t(e_1)(e_2)}$.
  \end{itemize}
\end{elidableproof}

>>>>

\section{Invariant-Confluence}

In this section, we present six different ways to think about
invariant-confluence: three state-based approaches and three operation-based
approaches.

\subsection{State-Based}
\begin{definition}
  A \defword{distributed state-based object} $O$ is a pair $(S, \join)$ where
  $S$ is a set of states, and $\join: S \times S \to S$ is a binary merge
  operator that we call join.
\end{definition}

@@

\begin{example}
  $(\nats, +)$ is a distributed object, $t(x) = 2x$ is a transaction, and
  $\setst{x \in \nats}{\text{$x$ is even}}$ is an invariant. Here, $I(0)$ and
  $I(2)$ but $\lnot I(1)$ and $\lnot I(3)$.
\end{example}

There are three ways to think about state-based invariant-confluence: a
process-based approach, a graph-based approach, and an expression-based
approach. Below, we describe the process-based approach and the graph-based
approach informally and describe the expression-based approach formally. All
three approaches are illustrated in \figref{StateBasedModels}.

@@

\subsubsection{Process-Based}
The process-based model is most similar to the process model described by
Shapiro et al.\ in~\cite{shapiro2011conflict}. We are given a state-based
object $O = (S, \join)$, a start state $s_0 \in S$, a set of transactions $T$,
an invariant $I$, and a set $\seq{p}{1}{n}$ of $n$ processors. Each processor
begins with state $s_0$. A processor $p_i$ can perform one of two actions.

@@

$O$ is invariant-confluent with respect to $s_0$, $T$, and $I$ (abbreviated $O$
is \sTIconfluent{}) if every reachable state (including $s_0$) satisfies the
invariant. Note that this definition of invariant-confluence is different from
the original definition in~\cite{bailis2014coordination}. Later, we will see
that they are equivalent.

\subsubsection{Graph-Based}
The graph-based approach is most similar to the model used by Bailis et al.\
in~\cite{bailis2014coordination}. We are given a directed acyclic graph where
vertices are states, and edges are either labelled with transactions or are
unlabelled if they correspond to a join. The graph is really just an alternate
way of representing an execution in the process-based model, but with duplicate
states collapsed into a single vertex. As with the process-based model, we say
that $O$ is \sTIconfluent{} if every vertex in every graph satisfies the
invariant.

\subsubsection{Expression-Based}
The expression-based approach formalizes the process-based and graph-based
approach using expressions. Given a state based object $O = (S, \join)$ and a
set of transactions $T$, we consider expressions generated by the following
grammar:
\[
  e ::= s \mid t(e) \mid e_1 \join e_2
\]
where $s$ correspond to a state in $S$ and $t$ corresponds to a transaction in
$T$. We can evaluate an expression $e$, written $eval(e)$, in the obvious way:
\begin{mathpar}
  eval(s) \defeq s

@@

\begin{definition}
  We say an expression is \defword{$\sTIreachable{}$} if it can be reached in
  an execution of the process-based model with starting state $s_0$,
  transactions $T$, and invariant $I$. Formally, we defined a predicate
  $\sTIreachable{}$ as follows:

  \begin{mathpar}
    \inferrule{ }{\sTIreachable{s_0}}

    \inferrule{\sTIreachable{e} \\ t \in T \\ I(t(e))}{\sTIreachable{t(e})}

    \inferrule{\sTIreachable{e_1} \\ \sTIreachable{e_2}}
              {\sTIreachable{e_1 \join e_2}}
  \end{mathpar}

  We say a state us $\sTIreachable{}$ if there exists an $\sTIreachable{}$
  expression $e$ such that $eval(e) = s$.
\end{definition}

\begin{definition}
  $O$ is \defword{\sTIconfluent{}} if $\setst{s}{\sTIreachable{s}} \subseteq
  I$. In other words, $T$ is \sTIconfluent{} if all $\sTIreachable{}$ states
  satisfy the invariant.
\end{definition}

As we mentioned earlier, this definition of \sTIconfluence{} is different than
the original definition presented in~\cite{bailis2014coordination} (though it
is the same as the definition in~\cite{gotsman2016cause}), but they are
(almost) equivalent. We introduce some definitions and then prove this.

\begin{definition}
  An expression $e$ \defword{recursively satisfies $I$}, denoted $\Irec{e}$, if
  $e$ and all of $e$'s children satisfy $I$. That is,
  \begin{mathpar}
    \inferrule{I(s)}{\Irec{s}}

@@

Bailis et al.\ defined \sTIconfluence{} to mean that all $\sTIreachable{}$
expressions recursively satisfying $I$ are closed under join. That is, $O$ is
\sTIconfluent{} if
\[
  \forall e_1, e_2 \in \setst{e}{\sTIreachable{e}}.\;
    \Irec{e_1} \land \Irec{e_2} \implies I(e_1 \join e_2)
\]
If $\lnot I(s_0)$, then invariant-confluence holds vacuously which is a bit
silly, so Bailis et al.\ probably ought to have also added the condition
$I(s_0)$ to their definition of invariant-confluence. Doing so, the two
definitions become equivalent.

\begin{claim}\clmlabel{StateBasedTwoIconfluenceDefs}
  Consider a state based object $O = (S, \join)$, a start state $s_0$, a set of
  transactions $T$, and an invariant $I$. The following two are equivalent:
  \begin{enumerate}[\quad(1)]
    \item
      $\setst{s}{\sTIreachable{s}} \subseteq I$

    \item
      $I(s_0)$ and
      $\forall e_1, e_2 \in \setst{e}{\sTIreachable{e}}.\;
         \Irec{e_1} \land \Irec{e_2} \implies I(e_1 \join e_2)$
  \end{enumerate}
\end{claim}
\begin{elidableproof}
  First, we show that (1) implies (2). Axiomatically, $\sTIreachable{s_0}$, so
  by (1), $I(s_0)$. Let $e_1$ and $e_2$ be arbitrary $\sTIreachable{}$
  expressions. Let $s_1 = eval(e_1)$ and $s_2 = eval(e_2)$. $e_1 \join e_2$ is
  $\sTIreachable{}$, so $s_1 \join s_2$ is $\sTIreachable{}$, so by (1), $I(s_1
  \join s_2)$, so $I(e_1 \join e_2)$.

  Next, we show that (2) implies (1). We prove by structural induction that for
  all $e$, $\sTIreachable{e} \implies \Irec{e}$. From this, (1) is immediate.
  \begin{itemize}
    \item \textbf{Case $s_0$.}
      $I(s_0)$ by (2), so $\Irec{s_0}$

    \item \textbf{Case $t(e)$.}
      Let $t(e)$ be $\sTIreachable{}$. Then, $\sTIreachable{e}$ and $I(t(e))$.
      By the inductive hypothesis, $\Irec{e}$, so by the definition of
      $\Irec{\cdot}$, $\Irec{t(e)}$.

    \item \textbf{Case $e_1 \join e_2$.}
      Let $e_1 \join e_2$ be $\sTIreachable{}$. Then, $\sTIreachable{e_1}$ and
      $\sTIreachable{e_2}$.  By the inductive hypothesis, $\Irec{e_1}$ and
      $\Irec{e_2}$. By $(2)$, $I(e_1 \join e_2)$. Thus, by the definition of
      $\Irec{\cdot}$, $\Irec{e_1 \join e_2}$.
  \end{itemize}
\end{elidableproof}

\subsection{Operation-Based}
\begin{definition}
  A \defword{distributed operation-based object} is a set $O = S$ of states.
\end{definition}

@@

\begin{example}
  $\nats$ is a distributed operation-based object. $t(x) = \lambda y.\ x + y$
  is a transaction that given a state $x$ returns a function $\lambda y.\ x +
  y$ that adds $x$ to its argument. $\setst{x \in \nats}{x \geq 0}$ is an
  invariant.
\end{example}

As with state-based objects, there are three ways to think about
operation-based invariant-confluence: a process-based approach, a graph-based
approach, and an expression-based approach. All three approaches are
illustrated in \figref{OpBasedModels} and are described in more detail below.

@@

\subsubsection{Process-Based}
As with the state-based approach, the process-based model is most similar to
the process model described by Shapiro et al.\ in~\cite{shapiro2011conflict}.
We are given an operation-based object $O$, a start state $s_0$, a set of
transactions $T$, an invariant $I$, and a set $\seq{p}{1}{n}$ of $n$
processors. Each processors begins with state $s_0$. A processor $p_i$ can do
one of two things.

@@

  \item
    $p_i$ can receive a broadcast shadow transaction $t(s_j)$ from some other
    processor $p_j$. When $p_i$ receives $t(s_j)$, it transitions from its
    state $s_i$ to state $t(s_j)(s_i)$. When $p_i$ receives a shadow
    transaction, it must execute it, even if $\lnot I(t(s_j)(s_i))$.
\end{itemize}

$O$ is \sTIconfluent{} if every reachable state (including $s_0$) satisfies the
invariant.

\subsubsection{Graph-Based}
In the graph-based model, we are given a directed acyclic graph in which each
vertex is a state $s$ and each edge is labelled with a shadow operation $t(s)$
where $s$ is some other vertex in the graph. $(O, T)$ is \sTIconfluent{} if
every vertex in every graph satisfies $I$.

\subsubsection{Expression-Based}
Given an operation-based object $O = S$ and a set of transactions $T$, we
consider expressions built from the following grammar:
\[
  e ::= s \mid t(e_1)(e_2)
\]
where $s$ corresponds to a state in $S$ and $t$ corresponds to a transaction in
$T$. We can evaluate an expression, denoted $eval(e)$, in the obvious way:
\begin{mathpar}
  eval(s) \defeq s

@@

\begin{definition}
  As with state-based expressions, we formalize which operation-based
  expressions are $\sTIreachable{}$.

  \begin{mathpar}
    \inferrule{ }{\sTIreachable{s_0}}

    \inferrule{
      \sTIreachable{e_1} \\
      \sTIreachable{e_2} \\
      t \in T \\
      I(t(e_1)(e_1))
    }{\sTIreachable{t(e_1)(e_2)}}
  \end{mathpar}

  Similarly, a state $s$ is $\sTIreachable{}$ if there exists an
  $\sTIreachable{}$ expression $e$ such that $eval(e) = s$.
\end{definition}

\begin{definition}
  $O$ is \defword{\sTIconfluent{}} if $\setst{s}{\sTIreachable{s}} \subseteq I$.
\end{definition}

As with state-based objects, we have an equivalent definition of
\sTIconfluence{} that deals with the closure of recursively invariant
satisfying states that are $\sTIreachable{}$.

@@

\begin{claim}\clmlabel{OpBasedTwoIconfluenceDefs}
  Given an operation-based object $O = S$, a start sate $s_0$, a set of
  transactions $T$, and an invariant $I$, the following two are equivalent:
  \begin{enumerate}[\quad(1)]
    \item
      $\setst{s}{\sTIreachable{s}} \subseteq I$

    \item
      $I(s_0)$ and
      $\forall e_1, e_2 \in \setst{e}{\sTIreachable{e}}.\;
       \forall t \in T.\;
        \Irec{e_1} \land \Irec{e_2} \land I(t(e_1)(e_1)) \implies
        I(t(e_1)(e_2))$.
  \end{enumerate}
\end{claim}
\begin{elidableproof}
  First, we show that (1) implies (2). $\sTIreachable{s_0}$, so by (1),
  $I(s_0)$. Let $e_1$ and $e_2$ be arbitrary $\sTIreachable{}$ expressions and
  $t$ be an arbitrary transaction in $T$ such that $\Irec{e_1}$, $\Irec{e_2}$,
  and $I(t(e_1)(e_1))$. Let $s_1 = eval(e_1)$ and $s_2 = eval(e_2)$.
  $\sTIreachable{t(e_1)(e_2)}$, so $\sTIreachable{t(s_1)(s_2)}$, so by (1),
  $I(t(s_1)(s_2))$, so $I(t(e_1)(e_2))$.

  Next, we show that (2) implies (1). We show by structural induction that for
  all $e$, $\sTIreachable{e} \implies \Irec{e}$. From this, (1) is immediate.
  \begin{itemize}
    \item \textbf{Case $s_0$.}
      By (2), $I(s_0)$, so $\Irec{s_0}$.

    \item \textbf{Case $t(e_1)(e_2)$.}
      Let $t(e_1)(e_2)$ be $\sTIreachable{}$. Then, $\sTIreachable{e_1}$,
      $\sTIreachable{e_2}$, and $I(t(e_1)(e_1))$. By the inductive hypothesis,
      $\Irec{e_1}$ and $\Irec{e_2}$. By (2), $I(t(e_1)(e_2))$, so
      $\Irec{t(e_1)(e_2)}$.
  \end{itemize}
\end{elidableproof}
